### 2017-01-17 MSSM/MSSM.tex
One more change...

\section{Background estimation}
\label{sec:mssm_bkgs}
The methods used for background estimation will be described in this
section.

>>>>

\section{Background estimation}
\label{sec:mssm_bkgs}
To estimate the backgrounds to the analysis a mixture of data--driven
methods and \ac{MC} samples is employed. The methods used for background 
estimation will be described in this section.
